draftFiguresPaper

### 2025-10-24 draftFiguresPaper.Rmd
cleaning-up dataset and adding TWN HKG

# 2) get total papers by country
papers_by_country <- datasetClassificationCountries_long_clean %>%
  group_by(iso3, .drop = F) %>% 
  count(iso3, name = "n_papers") %>%
  arrange(desc(n_papers)) %>% 
  merge(., incomeGroups, by.x = "iso3", by.y = "Code", all.x = T, all.y = F)

@@

@@

@@

papers_by_country_pollution_filteredUN_survey <- merge(papers_by_country_pollution_filteredUN, surveys_by_country, by = "iso3", all.x = T, all.y = T)

papers_by_country_pollution_filteredUN_survey$n_surveys <- ifelse(is.na(papers_by_country_pollution_filteredUN_survey$n_surveys), 0, papers_by_country_pollution_filteredUN_survey$n_surveys)

@@

summaryDataset <- merge(papers_by_country_pollution_filteredUN_survey, popCtr, by.x = "iso3", by.y = "GADM_ISO", all.x = T, all.y = F)

summaryDataset$categoryPollution <- cut(summaryDataset$pm25Avg, breaks = c(0, 10, 15, 25, 35, 100), 
                  labels = c("very low", "low", "medium", "high", "very high"), 
                  right = FALSE)

@@

# add region from natural earth

>>>>

# 2) get total papers by country
papers_by_country <- datasetClassificationCountries_long_clean %>%
  group_by(iso3, .drop = F) %>% 
  count(iso3, name = "n_papers") %>%
  arrange(desc(n_papers))

@@

datasetPollution_avg <- datasetPollution %>% 
  filter(Year %in% 2019) %>%
  group_by(Region) %>% 
  summarize(pm25Avg = mean(Population.Weighted.PM2.5..ug.m3., na.rm=T))

datasetPollution2 <- read.csv("dataNew/GlobalPM25-V5GL0502-Annual-1998-2023-wThresFrac.csv")

datasetPollution2_avg <- datasetPollution2 %>% 
  filter(Year %in% 2019) %>%
  filter(Region %in% c("Hong Kong", "Taiwan")) %>% 
  group_by(Region) %>% 
  summarize(pm25Avg = mean(Population.Weighted.PM2.5..ug.m3., na.rm=T))

datasetPollution_avg <- rbind(datasetPollution_avg, datasetPollution2_avg)

@@

# iso3_un_members <- c(
#   "AFG","ALB","DZA","AND","AGO","ATG","ARG","ARM","AUS","AUT","AZE",
#   "BHS","BHR","BGD","BRB","BLR","BEL","BLZ","BEN","BTN","BOL","BIH",
#   "BWA","BRA","BRN","BGR","BFA","BDI","CPV","KHM","CMR","CAN","CAF",
#   "TCD","CHL","CHN","COL","COM","COG","COD","CRI","CIV","HRV","CUB",
#   "CYP","CZE","DNK","DJI","DMA","DOM","ECU","EGY","SLV","GNQ","ERI",
#   "EST","SWZ","ETH","FJI","FIN","FRA","GAB","GMB","GEO","DEU","GHA",
#   "GRC","GRD","GTM","GIN","GNB","GUY","HTI","HND","HUN","ISL","IND",
#   "IDN","IRN","IRQ","IRL","ISR","ITA","JAM","JPN","JOR","KAZ","KEN",
#   "KIR","PRK","KOR","KWT","KGZ","LAO","LVA","LBN","LSO","LBR","LBY",
#   "LIE","LTU","LUX","MDG","MWI","MYS","MDV","MLI","MLT","MHL","MRT",
#   "MUS","MEX","FSM","MDA","MCO","MNG","MNE","MAR","MOZ","MMR","NAM",
#   "NRU","NPL","NLD","NZL","NIC","NER","NGA","MKD","NOR","OMN","PAK",
#   "PLW","PAN","PNG","PRY","PER","PHL","POL","PRT","QAT","ROU","RUS",
#   "RWA","KNA","LCA","VCT","WSM","SMR","STP","SAU","SEN","SRB","SYC",
#   "SLE","SGP","SVK","SVN","SLB","SOM","ZAF","SSD","ESP","LKA","SDN",
#   "SUR","SWE","CHE","SYR","TJK","TZA","THA","TLS","TGO","TON","TTO",
#   "TUN","TUR","TKM","TUV","UGA","UKR","ARE","GBR","USA","URY","UZB",
#   "VUT","VEN","VNM","YEM","ZMB","ZWE"
# )

# papers_by_country_pollution_filteredUN <- subset(papers_by_country_pollution, iso3 %in% iso3_un_members) %>% 
#   filter(!is.na(iso3))

@@

papers_by_country_pollution_survey <- merge(papers_by_country_pollution, surveys_by_country, by = "iso3", all.x = T, all.y = T)

papers_by_country_pollution_survey$n_surveys <- ifelse(is.na(papers_by_country_pollution_survey$n_surveys), 0, papers_by_country_pollution_survey$n_surveys)

@@

summaryDataset <- merge(papers_by_country_pollution_survey, popCtr, by.x = "iso3", by.y = "GADM_ISO", all.x = T, all.y = F)

summaryDataset$categoryPollution <- cut(summaryDataset$pm25Avg, breaks = c(0, 5, 10, 15, 25, 35, 100), 
                  labels = c("no pol", "very low", "low", "medium", "high", "very high"), 
                  right = FALSE)

summaryDataset <- merge(summaryDataset, incomeGroups, by.x = "iso3", by.y = "Code", all.x = T, all.y = F)

@@

## add region from natural earth
